---
title: "W6_Wed_Lab"
author: "Kirill Musaev"
date: "3/3/2021"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This is a **table** and **graphic** representation of mass of penguins of different species, grouped by island and sex

# Load libraries
We will need **libraries** for:

1. Dataset ( _penguins_ )
2. Formatting ( _tidyverse_ , _kableExtra_ ) and 
3. File management ( _here_ )
```{r libs, message = FALSE, warning = FALSE}
library(palmerpenguins)
library(tidyverse)
library(here)
library(kableExtra)
```

# Process data
Arranging the necessary data and calculating mean and variance of mass for the assigned groups. Commentary for each line is included
```{r data, echo = FALSE}
glimpse(penguins) #look at data structure

mean_and_var <- penguins %>% #create pipeline for calculating mean and variance
  group_by(species, island, sex) %>% #assign groups to work with
  drop_na(sex, body_mass_g, island, species) %>% #exclude NA variables
  summarise (mean_mass = mean(body_mass_g, na.rm = TRUE),
             var_mass = var(body_mass_g, na.rm = TRUE)#create and populate columns for mean and variance
  )
#view(mean_and_var)#check mean and variance calculations
```
# Create a table
Display calculated mean and variance values in a convenient way
```{r table, fig.path = "../Output/"}
knitr::kable(mean_and_var,
             col.names = c('Species', 'Island', 'Sex', 'Mean Mass (g)', 'Variance of Mass (g)')
) %>% #change column names to readable format
   kable_styling(full_width = F) #style width to fit all values

```

# Build a graph
Create a graph showing average mass difference between the 3 species. Adelie penguins are indicated separately for 3 islands.
```{r graph, fig.path = "../Output/"}
PenguinFigure <- penguins %>%
  ggplot(aes(x = species, y = flipper_length_mm, color = island)) + #set axes for the plot
  geom_boxplot()+
  labs(title = "Body Mass of Three Species of Penguins", #main figure lable
       subtitle = "With boxplots", #secondary lable
       caption = "Source: Palmer Station LTER / palmerpenguins package", #bottom lable
       x = "Species", 
       y = "Body mass, g",#axes lables
       color = "Island") #legend lable

PenguinFigure
```

