---
title: "W8_Wed_Lab"
author: "Kirill Musaev"
date: "3/29/2021"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
#(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
```

## Load libraries

```{r libs}
library(tidyverse)
library(here)
library(palmerpenguins)
```

## Define functions

### Filter function

This function will select either male or female penguins. This example selects females. Runs the function in the end and displays the filtered data

```{r filter_function}
#glimpse(penguins) #check data structure

temp_df <- penguins #create a new dataframe to work with to keep the original data intact

m_or_f <- function(temp_df, select_females) { #name a new function and set inputs
  if(select_females == TRUE) { #define what happens when selection for females is true
    filter(temp_df, sex == "female", na.rm = TRUE) #select females only and filter out NA values
  }
  else { #define what happens when selection for females is not true
    filter(temp_df, sex == "male", na.rm = TRUE) #select males only and filter out NA values
  }
}

filtered_data <- m_or_f(temp_df, select_females = TRUE) #execute the function and write processed data to a new dataframe
glimpse(filtered_data) #check that data was processed correctly
```

### Plot function

Allows to choose between boxplot and violin plot

```{r plot_function}
plot <- function(data = filtered_data, x, y, boxplot) { #name a function for plotting and specify inputs
  if(boxplot == TRUE) { #actions for when boxplot is set to true
  ggplot(data, aes(x = {{x}}, y = {{y}})) + #load data and specify axes
      geom_boxplot() + #add boxplot
      labs(x = "Island", #add labels and title
           y = "Body mass (g)",
           title = "Mass of penguins on three islands, box plot") +
      theme_bw() #change theme
  }
  else { #actions for when boxplot is not set to true
    ggplot(data, aes(x = {{x}}, y = {{y}})) +
      geom_violin() + #add violin plot
      labs(x = "Island", #add labels and title
           y = "Body mass (g)",
           title = "Mass of penguins on three islands, violin plot") +
      theme_bw() #change theme
  }
}

```

#### Build plots using the plot function. The plots represent body mass distribution of penguins on different islands

```{r f_boxplot}
plot(y = body_mass_g, x = island, boxplot = TRUE) + #use plot function
  labs(subtitle = "Females") #indicate that the data is on females
  ggsave(here("Week_8","Output","Female penguins boxplot.jpg"),#save plot to file
       width = 5, height = 7) #adjust size
```

```{r f_violin_plot}
plot(y = body_mass_g, x = island, boxplot = FALSE) + #use plot function
  labs(subtitle = "Females") #indicate that the data is on females
  ggsave(here("Week_8","Output","Female penguins violin plot.jpg"),#save plot to file
       width = 5, height = 7) #adjust size
```

#### This chunk filters the data for males using the function above

```{r filter_for_males}
filtered_data <- m_or_f(temp_df, select_females = FALSE) #execute the function and rewrite the dataframe used for plotting, this time for male penguins
glimpse(filtered_data) #check that data was rewritten
```

#### Plot the data for male penguins using the functions above

```{r m_boxplot}
plot(y = body_mass_g, x = island, boxplot = TRUE) + #use plot function
  labs(subtitle = "Males") #indicate that the data is on male penguins
  ggsave(here("Week_8","Output","Male penguins boxplot.jpg"),#save plot to file
       width = 5, height = 7) #adjust size
```

```{r m_violin_plot}
plot(y = body_mass_g, x = island, boxplot = FALSE) + #use plot function
  labs(subtitle = "Males") #indicate that the data is on males
  ggsave(here("Week_8","Output","Male penguins violin plot.jpg"),#save plot to file
       width = 5, height = 7) #adjust size
```
