---
title: "Good plot - Bad plot"
author: "Kirill Musaev"
date: "3/19/2021"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, results = FALSE, message = FALSE)
```

# Load Libraries

-   "Tidyverse" for formatting
-   "Here" for file management

```{r libs}
library(tidyverse)
library(here)

```

# Load Data

-   From file

-   Includes a command to glimpse at the data in the end

```{r load_from_file}
FullData<-read_csv(here("good_plot-bad_plot","data","ikea.csv")) #load data from file path
#glimpse(FullData) #check data loading
```

# Select and filter data

-   Create a data frame with only the data to be processed

-   Filter out incomplete rows

-   Includes a command to view the data in the end

```{r cleanup}
CleanData<-FullData %>%
  select(price, depth, height, width)%>% #delete unnecessary columns
  filter(complete.cases(.)) #remove incomplete rows
#view(CleanData) #check data 
  
```

# Process data

-   Calculate the volume of the item in each row
-   Convert the original prices in Saudi Riyals to USD using the conversion rate on 4/20/2020, the day the data was generated. Reference: <https://www.exchange-rates.org/Rate/USD/SAR/4-20-2020>
-   Includes a command to view the data in the end

```{r calculations}
DataWVolume <- CleanData %>% #create pipeline for calculations
  mutate(volume = depth * height * width) %>% #calculate volume
  mutate(price = price / 3.7545) #convert currency

#view(DataWVolume) #check data
```

# Generate bad plot

-   Low resolution
-   Undescriptive title
-   Title does not fit in the image
-   Axes labels useless, no units
-   Y axis coordinates in an inconvenient notation
-   "Independent" variable on vertical axis
-   Box plot not appropriate for data that is continuous on both axes, effectively eliminating the x axis
-   Regression line is linear while one of the axes is logarithmic
-   Regression line color blends in with the background

```{r bad_plot, fig.width=2,fig.height=2}
DataWVolume %>% #pipeline for ggplot
  ggplot(aes(x = log10(price), #x axis irrelevant
             y = volume) #"independent" variable on y axis
  ) +
  geom_boxplot() + #graph type discontinuous on x axis
  geom_smooth(method = "lm", #regression line linear on a log graph
              colour = "azure") + #color blends in with the background
  labs(x = "Left-right",#useless labels
       y = "Up-down",
       title = "IKEA furniture size and price"
       )

ggsave(here("good_plot-bad_plot","Output","Bad_plot.jpg"),#save plot to file
       width = 1.5, height = 1.5) #set aspect ratio
```

# Generate good plot

-   Bulkier items tend to cost more
-   Use scatterplot to indicate all data points
-   Logarithmic scale due to large spread of weight
-   Trendline using LOWESS
-   Save output to file

```{r good_plot, fig.width=10,fig.height=9}
DataWVolume %>% #pipeline for ggplot
  ggplot(aes(x = log2(volume), #set x axis to volume and apply logarithmic scale
             y = price #set y axis to price
             )
         ) +
  geom_point(size = 1) + # set size for individual data points
  geom_smooth(method = "loess", #create regression line using local fitting
              se = FALSE, #remove confidence intervals since they are not rendered correctly on log scale
              colour = "coral") + #set color for regression line
  labs(x = "Volume, log₂ cm³",#set x axis label.Note that "₂" did not render as a subscript on the plot
       y = "Price, USD", #y axis label
       title = "Price of IKEA Items Correlates with Volume", #add title 
       subtitle = "Currency converted from Saudi Riyal (SAR) to United States Dollar (USD) using conversion \nrate as of 4/20/2020, the date that the dataset was generated", #add subtitle
       caption = "Source: Ahmed_k_Allam at Kaggle" #indicate source under the graph
       )+
  theme_light(base_size = 22) + #set a theme
  theme(plot.subtitle = element_text(size = 15)) #set size for subtitle

ggsave(here("good_plot-bad_plot","Output","Good_plot.jpg"),#save plot to file
       width = 10, height = 9) #set aspect ratio
```
